---
title: "R Notebook"
output: html_notebook
---

The [R plugin](https://www.jetbrains.com/help/pycharm/r-plugin-support.html) for IntelliJ-based IDEs provides
handy capabilities to work with the [R Markdown](https://www.jetbrains.com/help/pycharm/r-markdown.html) files.
To [add](https://www.jetbrains.com/help/pycharm/r-markdown.html#add-code-chunk) a new R chunk,
position the caret at any line or the code chunk, then click "+".

The code chunk appears:
```{r}
knitr::opts_chunk$set(echo = FALSE, error=F, warning=F)
library(tidyverse) # CSV file I/O, e.g. the read_csv function
library(RColorBrewer)
library(plotly)
library(tidyverse)
library(scales)
library(glue)
library(flametree)
```
```{r}
tibble(x1 = 1,
       y1 = 5,
       x2 = 6,
       y2 = -2) %>%
  ggplot()+
  geom_segment(aes(x = x1,
                   y = y1,
                   xend = x2,
                   yend = y2))+
theme_void()

```


Type any R code in the chunk, for example:
```{r}
 N<- 30
tibble(x1 = runif(N, -1, 1),
       y1 = runif(N, -1, 1),
       x2 = runif(N, -1, 1),
       y2 = runif(N, -1, 1)) %>%
  ggplot()+
  geom_segment(aes(x = x1, y = y1, xend = x2, yend = y2))+
  theme_void()+
  labs(subtitle = "Lines")
```

Now, click the **Run** button on the chunk toolbar to [execute](https://www.jetbrains.com/help/pycharm/r-markdown.html#run-r-code) the chunk code. The result should be placed under the chunk.
Click the **Knit and Open Document** to build and preview an output.
```{r}
N <- 30
cols <- rainbow(N)
cols <- c("#EF892D", "#FEC784", "#45555F", "#93ADC5", "#BF49DB")
#set.seed(43)
tibble(line = 1:N %% 5,
       x1 = runif(N, -1, 1),
       y1 = runif(N, -1, 1),
       x2 = runif(N, -1, 1),
       y2 = runif(N, -1, 1),
       size = runif(N, 0, 3),
       alpha = runif(N, 0.1, 0.9)) %>%
  ggplot()+
  geom_segment(aes(x = x1, y = y1, xend = x2, yend = y2, size = size, alpha = alpha, color = as.factor(line)),show.legend = FALSE)+
  scale_color_manual(values = cols)+
  scale_size_continuous(range = c(2,20))+
  theme_void()+
  labs(subtitle = "Rainbow Lines")
```
```{r}
seq(-2,2, by = 0.01) %>%
  expand.grid(x=., y=.) %>%
  ggplot(aes(x = x^3 - sin(y), y = y^3 - cos(x)))+
  geom_point(alpha = 0.05, color = "black", shape = 20, size = 0)+
  theme_void()+
  coord_polar()+
  labs(subtitle = "Dandelion")
```
```{r}



flametree_grow(seed = 4, time = 12, split = 2, angle = seq(-20,30,5), trees = 3) %>%
  flametree_plot(style = "nativeflora", background = "white") +
  annotate(geom = "text",x = 0, y = -1, label = "Made in R using `flametree` package", color = "white")
```
```{r}
shades <- c("#A06AB4", "#FFD743", "#07BB9C", "#D773A2")

flametree_grow(
  trees = 10,
  time = 7,
  shift_x = spark_random(multiplier = 1),
  shift_y = spark_random(multiplier = 1)
) %>%
  flametree_plot(palette = shades,background = "white", style = "nativeflora")
```
```{r}
seq(-12,12, by = 0.04) %>%
  expand.grid(x=., y=.) %>%
  ggplot(aes(x = x+pi*sin(y), y = y+ pi*sin(x)))+
  geom_point(alpha = 0.05, color = "red", shape = 20, size = 0)+
  theme_void()+
  coord_polar()+
  labs(subtitle = "Rose")
```
